\documentclass[12pt]{article}
% This is a list of the publications

\usepackage[letterpaper, portrait, margin=1in]{geometry}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{chemfig}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{etaremune}

\doublespacing

\begin{document}

\pagenumbering{gobble}

\section*{Refereed Journal Articles}

\begin{etaremune}

\item S. Mostafa Razavi, Richard A. Messerly, J. Richard Elliott. ``Coexistence Calculation Using the Isothermal-Isochoric Integration Method.'' \textit{Fluid Phase Equilibria.} Pending publication.

\item Richard A. Messerly, Michael R. Shirts, and Andrei F. Kazakov. ``Uncertainty quantification confirms unreliable extrapolation toward high pressures for united-atom Mie λ-6 force field.'' \textit{The Journal of Chemical Physics.} Pending publication.

\item Edward J. Maginn, Richard A. Messerly, Daniel J. Carlson, Daniel R. Roe, J. Richard Elliott. ``Best Practices for Computing Transport Properties 1. Self-Diffusivity and Viscosity from Equilibrium Molecular Dynamics v1.'' \textit{Living Journal of Chemical Physics.} Pending publication.
	
\item Richard A. Messerly, S. Mostafa Razavi, and Michael R. Shirts. ``Configuration-sampling-based surrogate models for rapid parameterization of non-bonded interactions.'' \textit{Journal of Chemical Theory and Computation.} Pending publication.
	
\item Richard A. Messerly, Thomas A. Knotts IV, and W. Vincent Wilding. ``Uncertainty quantification and propagation of errors of the Lennard-Jones 12-6 parameters for \textit{n}-alkanes.'' \textit{The Journal of Chemical Physics.} 146, 194110, 1-16, 2017.

\item Richard A. Messerly, Thomas A. Knotts IV, Neil F. Giles, and W. Vincent Wilding. ``Developing an internally consistent set of theoretically based prediction models for the critical constants and normal boiling point of large \textit{n}-alkanes.'' \textit{Fluid Phase Equilibria.} 449, 104-116, 2017.

\item Richard A. Messerly, Thomas A. Knotts IV, Richard L. Rowley, and W. Vincent Wilding. ``Improved estimates of the critical point constants for large \textit{n}-alkanes using Gibbs ensemble Monte Carlo simulations.'' \textit{Journal of Chemical \& Engineering Data.} 2016.

\item Richard A. Messerly, Thomas A. Knotts IV, Richard L. Rowley, and W. Vincent Wilding. ``An improved approach for predicting the critical constants of large molecules with Gibbs ensemble Monte Carlo simulation.'' \textit{Fluid Phase Equilibria.} 425, 432-442. 2016.

\item Richard A. Messerly. ``First Principles Prediction of the Copolymerization Process of 1,3-Butadiene and Vinyl Chloride.'' \textit{Journal of Theoretical \& Computational Science.} 3:142. 2016.

\item Richard A. Messerly, Richard L. Rowley, Thomas A. Knotts IV, and W. Vincent Wilding. ``An improved statistical analysis for predicting the critical temperature and critical density with Gibbs ensemble Monte Carlo simulation.'' \textit{Journal of Chemical Physics.} 143, 104101, 1-8. 2015.



\end{etaremune}

\section*{Presentations}

\begin{etaremune}
	
\item Richard A Messerly. ``Accelerating Force Field Parameterization to Improve the Quantitative Predictability of Thermophysical Properties.'' \textit{American Institute of Chemical Engineers Annual Meeting.} Minneapolis, Minnesota. 2017.
	
\item Richard A Messerly. ``Pushing the Frontier of Data-Driven Force Field Development.'' \textit{Thermodynamics Research Center Consortium.} Boulder, Colorado. 2017.
	
\item Richard A Messerly. ``A Novel Force Field Development Algorithm to Improve the Quantitative Predictability of Thermophysical Properties with Molecular Simulation.'' \textit{European Symposium on Applied Thermodynamics 2017.} Bucharest, Romania. 2017.

\item Richard A Messerly. ``How Uncertainty Quantification Renders Molecular Simulation a Quantitative Tool for Thermophysical Property Evaluation.'' \textit{American Institute of Chemical Engineers Annual Meeting.} San Francisco, California. 2016.

\item Richard A Messerly. ``Uncertainty Quantification of Intermolecular Parameters with a Transferable Potential Model for \textit{n}-Alkanes.'' \textit{American Institute of Chemical Engineers Annual Meeting.} San Francisco, California. 2016.

\item Richard A Messerly. ``Uncertainty Quantification and Propagation Associated with a Transferable Intermolecular Potential Model for \textit{n}-Alkanes.'' \textit{International Conference on Properties and Phase Equilibria for Product and Process Design.} Porto, Portugal. 2016.

\item Richard A Messerly. ``A Statistical Analysis of the Propagation of Error Associated with the Intermolcular Potential Model When Simulating Large Compounds.'' \textit{American Institute of Chemical Engineers Annual Meeting.} Salt Lake City, Utah. 2015.

\item Richard A Messerly. ``A Statistical Approach to Reducing Finite-Size Effects from Gibbs Ensemble Monte Carlo Simulations for Predicting the Critical Point.'' \textit{American Institute of Chemical Engineers Annual Meeting.} Salt Lake City, Utah. 2015.

\item Richard A Messerly. ``Group Contribution Model for Predicting Critical Volume with the Flory-Huggins Theory Asymptotic Behavior.'' \textit{19 $^{th}$ Symposium on Thermophysical Properties.} Boulder, Colorado. 2015.

\item Richard A Messerly. ``Molecular Simulations of the Critical Point for Molecules That Decompose Experimentally.'' \textit{American Institute of Chemical Engineers Annual Meeting.} Atlanta, Georgia. 2014.

\end{etaremune}



\end{document}