\documentclass[12pt]{article}
% This is a list of the publications

\usepackage[letterpaper, portrait, margin=1in]{geometry}
\usepackage{cite}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{chemfig}
\usepackage{indentfirst}
\usepackage{setspace}
\usepackage{etaremune}

%\doublespacing

\title{Complete list of publications of Richard Messerly}
\date{}

\renewcommand\thesection{\Alph{section}}

\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}

\begin{document}

\maketitle

\pagenumbering{gobble}

\section*{Further publications}

\section{Publications with peer review process}

\begin{enumerate}
	
\item \textbf{Richard A. Messerly}$^*$, S. Mostafa Razavi, and Michael R. Shirts. ``Configuration-sampling-based surrogate models for rapid parameterization of non-bonded interactions.'' \textit{Journal of Chemical Theory and Computation.} 14 (6), 3144-3162, 2018.
	
\item \textbf{Richard A. Messerly}$^*$, Thomas A. Knotts IV, and W. Vincent Wilding. ``Uncertainty quantification and propagation of errors of the Lennard-Jones 12-6 parameters for \textit{n}-alkanes.'' \textit{The Journal of Chemical Physics.} 146, 194110, 1-16, 2017.

\item \textbf{Richard A. Messerly}$^*$, Thomas A. Knotts IV, Neil F. Giles, and W. Vincent Wilding. ``Developing an internally consistent set of theoretically based prediction models for the critical constants and normal boiling point of large \textit{n}-alkanes.'' \textit{Fluid Phase Equilibria.} 449, 104-116, 2017.

\item \textbf{Richard A. Messerly}$^*$, Thomas A. Knotts IV, Richard L. Rowley, and W. Vincent Wilding. ``Improved estimates of the critical point constants for large \textit{n}-alkanes using Gibbs ensemble Monte Carlo simulations.'' \textit{Journal of Chemical \& Engineering Data.} 61 (10), 3640-3649, 2016.

\item \textbf{Richard A. Messerly}$^*$, Thomas A. Knotts IV, Richard L. Rowley, and W. Vincent Wilding. ``An improved approach for predicting the critical constants of large molecules with Gibbs ensemble Monte Carlo simulation.'' \textit{Fluid Phase Equilibria.} 425, 432-442. 2016.

\item \textbf{Richard A. Messerly}$^*$. ``First Principles Prediction of the Copolymerization Process of 1,3-Butadiene and Vinyl Chloride.'' \textit{Journal of Theoretical \& Computational Science.} 3:142. 2016.

\item Joseph W. Hogge$^*$, \textbf{Richard A. Messerly}, Neil Giles, Thomas Knotts, Richard Rowley, W. Vincent Wilding. ``Improving Thermodynamic Consistency Among Vapor Pressure, Heat of Vaporization, and Liquid and Ideal Gas Isobaric Heat Capacities through Multi{-}Property Optimization.'' \textit{Fluid Phase Equilibria.} 418, 37-43, 2016.

\item \textbf{Richard A. Messerly}$^*$, Richard L. Rowley, Thomas A. Knotts IV, and W. Vincent Wilding. ``An improved statistical analysis for predicting the critical temperature and critical density with Gibbs ensemble Monte Carlo simulation.'' \textit{Journal of Chemical Physics.} 143, 104101, 1-8, 2015.

\item Joseph C. Bell$^*$, \textbf{Richard A. Messerly}, Ryan Gee, Aaron Harrison, Richard L. Rowley, and W. Vincent Wilding. ``Ternary Liquid{-}Liquid Equilibrium of Biodiesel Compounds for Systems Consisting of a Methyl Ester + Glycerin + Water.'' \textit{Journal of Chemical \& Engineering Data.} 58 (4), 1001-1004, 2013.

\end{enumerate}

\section{Submitted publications with peer review process}

\begin{enumerate}
	
\item \textbf{Richard A. Messerly}$^*$, S. Mostafa Razavi, Michelle C. Anderson, J. Richard Elliott. ``Transferability of Mie n-6 force fields for predicting liquid shear viscosity at saturation and elevated pressures.'' \textit{Special Issue: Fluid Phase Equilibria.} (publisher's acknowledgment of receipt enclosed).
	
\item S. Mostafa Razavi$^*$, \textbf{Richard A. Messerly}, J. Richard Elliott. ``Coexistence Calculation Using the Isothermal-Isochoric Integration Method.'' \textit{Special Issue: Fluid Phase Equilibria.} (publisher's acknowledgment of receipt enclosed).

\item \textbf{Richard A. Messerly}$^*$, Michael R. Shirts, and Andrei F. Kazakov. ``Uncertainty quantification confirms unreliable extrapolation toward high pressures for united-atom Mie $\lambda$-6 force field.'' \textit{The Journal of Chemical Physics.} (publisher's acknowledgment of receipt enclosed)

\item Edward J. Maginn, \textbf{Richard A. Messerly}$^*$, Daniel J. Carlson, Daniel R. Roe, J. Richard Elliott. ``Best Practices for Computing Transport Properties 1. Self-Diffusivity and Viscosity from Equilibrium Molecular Dynamics v1.'' \textit{Living Journal of Computational Molecular Science.} (publisher's acknowledgment of receipt enclosed)

\end{enumerate}

\section*{* = Corresponding author}

\textbf{The following above mentioned publications have evolved from my doctoral dissertation:} A2, A3, A4, A5, A8

\blfootnote{as of July 2018}

\end{document}